Syllabus

### 2019-08-14 content/_index.Rmd
Updated learning goals

1. understand how to evaluate statistical and empirical claims;
2. use the fundamental models of causal inference and research design;
2. gather, analyze, and communicate with real data in R.

>>>>

1. understand how to evaluate statistical and empirical claims;
2. use the fundamental models of causal inference and research design;
3. gather, analyze, and communicate with real data in R.

Given these objectives, this course fulfills all three of the learning outcomes for [the George B. Delaplaine, Jr. School of Business](https://www.hood.edu/academics/departments/george-b-delaplaine-jr-school-business/student-learning-outcomes) Economics B.A. program:

- Use quantitative tools and techniques in the preparation, interpretation, analysis and presentation of data and information for problem solving and decision making [...]
- Apply economic reasoning and models to understand and analyze problems of public policy [...]
- Demonstrate effective oral and written communications skills for personal and professional success[...]

### 2019-08-14 content/syllabus.Rmd
Updated learning goals

1. understand how to evaluate statistical and empirical claims;
2. use the fundamental models of causal inference and research design;
2. gather, analyze, and communicate with real data in R.

@@

Given these objectives, this course fulfills three of the four learning outcomes for BYU's [Master of Public Administration (MPA)](https://marriottschool.byu.edu/mpa/) program:

- **Quantitative Analysis**: BYU MPA graduates are skilled at evaluating programs and policies. They know how to gather data, correctly analyze it, and employ the analysis to recommend policy and programmatic action in public service organizations.
- **Public Service Values**: BYU MPA graduates demonstrate an understanding of, passion for, and commitment to public service values, including reverence for the dignity and worth of all people and dedication to ethical governance.
- **Communication**: BYU MPA graduates effectively convey verbal and written information with the polish and professionalism appropriate for the public service context. They listen to and promote understanding among people with diverse viewpoints.

>>>>

1. understand how to evaluate statistical and empirical claims;
2. use the fundamental models of causal inference and research design;
3. gather, analyze, and communicate with real data in R.

@@

Given these objectives, this course fulfills all three of the learning outcomes for [the George B. Delaplaine, Jr. School of Business](https://www.hood.edu/academics/departments/george-b-delaplaine-jr-school-business/student-learning-outcomes) Economics B.A. program:

- Use quantitative tools and techniques in the preparation, interpretation, analysis and presentation of data and information for problem solving and decision making [...]
- Apply economic reasoning and models to understand and analyze problems of public policy [...]
- Demonstrate effective oral and written communications skills for personal and professional success[...]
